%-------------------------
% Resume in Latex
% Author : Ramdev C M
% Website: https://ramdevcm.github.io/
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}M}
  \textbf{\href{http://ramdevcm.github.io/}{\Large Ramdev C M}} & Email : \href{mailto:ramdevcm@gmail.com}{ramdevcm@gmail.com}\\
  \href{https://ramdevcm.github.io/}{ramdevcm.github.io} & LinkedIn: \href{https://www.linkedin.com/in/ramdevcm/} {@ramdevcm} \\
  +91 8547825416 & GitHub: \href{https://github.com/ramdevcm}{@ramdevcm}
  
\end{tabular*}

\section{Field of Interest }
    Site Reliability Engineering
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vimal Jyothi Engineering College}{Kannur, Kerala}
      {Bachelor of Technology in Computer Science and Engineering;  CGPA: 8.00}{Aug. 2018 -- present}
    \resumeSubheading
      {Marygiri Senior Secondary School}{Kannur, Kerala}
      {All India Senior Certificate Examination (CBSE) (79\%)}{June. 2016 -- June. 2018}
   \resumeSubheading
      {St. Anne's English Medium School}{Kannur, Kerala}
      {Indian Certificate of Secondary Education Examination (ICSE) (84\%)}{June. 2006 -- June. 2018}
  \resumeSubHeadingListEnd

\setlist[itemize]{leftmargin=2.5cm}

%-----------EXPERIENCE-----------------
\section{Experience \& Internships}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Cell, VJEC}{Kannur, Kerala}
      {Android Front-end Developer} {Aug 2020 - Present \\* } 
      
        \vspace{1mm}\hspace{1cm}\underline{Key Qualifications \& Responsibilities:}
          \begin{itemize}
                \item Developed native Android application SYNC VJ using Java and XML.
                \item Defined and implemented robust app architectures and complex user interfaces.
                \item Wrote elegant, self-documenting code, easy to read and adapt for other developers.
                \item Reviewed design specs and engineering docs and provide feedback.
          \end{itemize}
          
        \hspace{1cm}\underline{Key Achievement:}
        \begin{itemize}
            \item Developed Sync VJ app which is currently used by entire staffs(60+) at VJEC (deployed at playstore).
            \item Received appreciation from entire management.
            
        \end{itemize}
        
    \resumeSubheading
      { }{ }
      {Back-end Web Developer}{ \\ \\ } 
      
      \hspace{1cm}\underline{Key Qualifications \& Responsibilities:}
          \begin{itemize}
                \item Responsible for full stack web development for all client projects.
                \item Resolved complex database architectures and implemented using SQL.
                \item Scaling website based on traffic.
          \end{itemize}
          
        \hspace{1cm}\underline{Key Achievement:}
        \begin{itemize}
            \item Developed VJSOFT website which was used by 10000+ people to collect data of 300000+ people (deployed in Bluehost).
            \item Received appreciation from entire management.
        \end{itemize}
      
      
    \resumeSubheading
      {ACM, VJEC}{Kannur, Kerala}
      {Website Developer \& Maintainer} {May 2021 - Present \\* } 
      
        \vspace{1mm}\hspace{1cm}\underline{Key Qualifications \& Responsibilities:}
          \begin{itemize}
            \item Developed web pages for event registrations
            \item Run frequent database checkups to filter and clean irrelevant threads
            \item Designing and developed an elegant web page for ACM-W
          \end{itemize}
          
        \hspace{1cm}\underline{Key Achievement:}
        \begin{itemize}
            \item ACM and ACM-w website which have 1000+ page click count (deployed in A2 Hosting).
        \end{itemize}
        
        
    \resumeSubheading
      {Intern, Microsoft}{Remote, Online}
      {Mastering Skillset} {July 2020 - August 2020 \\* } 
      
        \vspace{1mm}\hspace{1cm}\underline{Key Qualifications \& Responsibilities:}
          \begin{itemize}
              \item Campus to Corporate: Business Foundation Skills
              \item Campus to Corporate: Work Ready Skills
              \item Technical Engineer Skills
          \end{itemize}
          
        \hspace{1cm}\underline{Key Achievement:}
        \begin{itemize}
            \item Gained an understanding of how industry hires employees
        \end{itemize}
        
    \resumeSubheading
      {Intern, JPMorgan Chase \& Co}{Remote, Online}
      {Software Engineering} {December 2020 - January 2021 \\* } 
      
        \vspace{1mm}\hspace{1cm}\underline{Key Qualifications \& Responsibilities:}
          \begin{itemize}
              \item Interface with a stock price data feed
              \item Used JPMorgan Chase frameworks and tools 
              \item Display data visually for traders
          \end{itemize}
          
        \hspace{1cm}\underline{Key Achievement:}
        \begin{itemize}
            \item Absorbed hands on experience in data science using python
        \end{itemize}
        
    
    \resumeSubheading
      {Coding Blocks}{Remote, Online}
      {Campus Ambassador} {February 2021 - present \\* } 
      
        \vspace{1mm}\hspace{1cm}\underline{Key Qualifications \& Responsibilities:}
          \begin{itemize}
              \item Be the official Campus SuperHero and branding representative of Coding
Blocks in college.
              \item Conduct Coding Blocks Workshop/Webinars.
        
          \end{itemize}
          
        \hspace{1cm}\underline{Key Achievement:}
        \begin{itemize}
            \item Nominated for SuperHero of the month(March).
            \item Received swags and goodies. 
        \end{itemize}
        \resumeItemListEnd

%-------Certificates and Workshops ---------
\section{Certificates \& Workshops}
 \resumeSubHeadingListStart
   \item {
        \textbf{Google Cloud}{: Creating New BigQuery Datasets and Visualizing
Insights}
   }
   \hfill
   Feb 20, 2021
   
   \item {
        \textbf{Google Cloud}{: Exploring and Preparing your Data with BigQuery}
        \hfill
        Feb 20, 2021
   }
   \item {
        \textbf{Google Cloud}{: Applying Machine Learning to your Data with GCP}
        \hfill
        Feb 20, 2021
   }
   \item {
        \textbf{Google Cloud}{: Achieving Advanced Insights with BigQuery}
        \hfill
        Feb 20, 2021
   }
   \item {
        \textbf{Google}{: Crash Course on Python }
        \hfill
        Feb 20, 2021
   }
   \item{
        \textbf{Microsoft}{: AI Classroom Series}
        \hfill
        Dec 26, 2020
    }
   
   

  \resumeSubHeadingListEnd
 
 %-------Participation & Achievements---------
\section{Participation \& Achievements}
 \resumeSubHeadingListStart
   \item{
     \textbf{Website development(Front-end using React)}{: Runner in Design Jam 2.0 Conducted by SVCE ACM Student Chapter }
     \hfill
    
   }
 \resumeSubHeadingListEnd
 
 %-------Projects ---------
\definecolor{linkcolor}{RGB}{0, 5, 46}
\section{Projects (to be updated shortly)}
 \resumeSubHeadingListStart 
   \item{ Personal projects were Open Sourced and can be found in GitHub 
   \href{https://ggithub.com/ramdevcm/}{  \textcolor{linkcolor}{Click here}}\\
  }
  \item{
        SyncVJ - Android application (published in playstore) 
       \href{https://play.google.com/store/apps/details?id=com.VJEC.SyncVJ}{\textcolor{linkcolor}{Click here}}\\
  }
  \item{
        Vihi - (Zoom clone) using NodeJS (deployed in Heroku) \href{https://fast-hollows-20004.herokuapp.com/}{\textcolor{linkcolor}{Click here}}\\
  }
  \item{
        Epic - AR app(android) for college techfest  using Unity and Vuforia engine
        \href{https://drive.google.com/open?id=1OVTjpE2-qClA_W0ap8-5odSAC0bN4U3y}{\textcolor{linkcolor}{Click here}}\\
  }
  \item{ 
        Intelligent Map for Blind Students - Design Project 
        \href{https://drive.google.com/file/d/1xITPrZ94L_P1YpqtMC1kdv9Gz4hMPUxl/view?usp=sharing}{\textcolor{linkcolor}{Click here}}\\
  }
  \item {
        Private projects - cannot disclose
  }

 \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C++, SQL, Java, C, JavaScript}
    }
    \item{
    \textbf{Technologies}{: GCP, React, Azure, AWS, GitHub, GitLab, Heroku, XAMPP}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
